### 2014-10-09 LaTeX/mCitySimPlot.tex
handing it back to ben

% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:41
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,106.37) --
	( 61.01,109.04) --
	( 65.48,110.52) --
	( 65.62,110.57) --
	( 79.64,115.23) --
	( 88.50,118.17) --
	( 94.41,120.14) --
	( 97.84,121.27) --
	(104.50,123.49) --
	(110.01,125.32) --
	(113.94,126.62) --
	(116.56,127.49) --
	(124.94,130.28) --
	(160.01,141.93) --
	(160.15,141.97) --
	(163.56,143.10) --
	(164.50,143.42) --
	(175.08,146.93) --
	(177.68,147.80) --
	(185.12,150.27) --
	(195.04,153.56) --
	(195.05,153.57) --
	(199.79,155.14) --
	(200.09,155.24) --
	(201.70,155.77) --
	(202.42,156.01) --
	(203.15,156.26) --
	(203.24,156.29) --
	(203.92,156.51) --
	(204.08,156.56) --
	(205.70,157.10) --
	(211.30,158.97) --
	(213.02,159.54) --
	(213.22,159.60) --
	(213.28,159.62) --
	(214.88,160.15) --
	(219.39,161.65) --
	(219.87,161.81) --
	(224.51,163.35) --
	(226.38,163.97) --
	(226.89,164.14) --
	(228.22,164.58) --
	(229.80,165.11) --
	(230.53,165.35) --
	(231.54,165.69) --
	(232.29,165.94) --
	(232.55,166.02) --
	(232.60,166.04) --
	(233.03,166.18) --
	(236.50,167.34) --
	(238.44,167.98) --
	(239.50,168.33) --
	(240.76,168.75) --
	(242.87,169.45) --
	(243.82,169.77) --
	(244.87,170.11) --
	(245.90,170.46) --
	(247.14,170.87) --
	(247.15,170.87) --
	(248.00,171.16) --
	(248.59,171.35) --
	(249.15,171.54) --
	(249.91,171.79) --
	(250.14,171.87) --
	(250.71,172.06) --
	(251.21,172.22) --
	(251.61,172.35) --
	(251.88,172.44) --
	(252.52,172.66) --
	(252.98,172.81) --
	(253.12,172.85) --
	(253.36,172.94) --
	(254.91,173.45) --
	(255.02,173.49) --
	(256.32,173.92) --
	(258.61,174.68) --
	(260.03,175.15) --
	(260.14,175.19) --
	(260.80,175.41) --
	(261.97,175.79) --
	(262.19,175.87) --
	(262.48,175.96) --
	(262.99,176.14) --
	(264.29,176.57) --
	(264.50,176.64) --
	(264.53,176.65) --
	(264.97,176.79) --
	(266.10,177.17) --
	(266.13,177.18) --
	(266.44,177.28) --
	(267.28,177.56) --
	(267.71,177.70) --
	(268.38,177.92) --
	(269.11,178.17) --
	(269.74,178.38) --
	(269.87,178.42) --
	(271.02,178.80) --
	(271.10,178.83) --
	(271.68,179.02) --
	(272.40,179.26) --
	(272.79,179.39) --
	(273.63,179.67) --
	(274.52,179.96) --
	(275.28,180.22) --
	(275.59,180.32) --
	(276.13,180.50) --
	(276.31,180.56) --
	(276.77,180.71) --
	(277.30,180.89) --
	(277.98,181.12) --
	(278.04,181.13) --
	(278.45,181.27) --
	(279.17,181.51) --
	(279.30,181.55) --
	(279.52,181.62) --
	(279.66,181.67) --
	(279.69,181.68) --
	(280.15,181.83) --
	(280.53,181.96) --
	(280.72,182.02) --
	(281.20,182.18) --
	(281.36,182.24) --
	(281.45,182.27) --
	(282.80,182.71) --
	(283.05,182.80) --
	(283.89,183.08) --
	(283.98,183.11) --
	(284.07,183.14) --
	(284.62,183.32) --
	(284.86,183.40) --
	(285.03,183.46) --
	(285.13,183.49) --
	(286.00,183.78) --
	(286.57,183.97) --
	(286.59,183.98) --
	(287.25,184.19) --
	(287.81,184.38) --
	(288.54,184.62) --
	(288.59,184.64) --
	(289.22,184.85) --
	(289.76,185.03) --
	(290.76,185.36) --
	(290.86,185.39) --
	(291.20,185.51) --
	(291.32,185.54) --
	(291.81,185.71) --
	(291.88,185.73) --
	(292.21,185.84) --
	(292.36,185.89) --
	(292.42,185.91) --
	(292.49,185.93) --
	(292.51,185.94) --
	(292.62,185.98) --
	(293.21,186.17) --
	(293.91,186.41) --
	(295.25,186.85) --
	(295.45,186.92) --
	(295.51,186.94) --
	(295.93,187.08) --
	(295.99,187.10) --
	(296.10,187.13) --
	(296.47,187.26) --
	(296.65,187.32) --
	(296.99,187.43) --
	(297.01,187.43) --
	(297.04,187.45) --
	(297.05,187.45) --
	(297.09,187.46) --
	(297.13,187.47) --
	(297.22,187.51) --
	(297.31,187.53) --
	(297.31,187.53) --
	(297.71,187.67) --
	(297.96,187.75) --
	(298.34,187.88) --
	(298.57,187.95) --
	(299.04,188.11) --
	(300.58,188.62) --
	(300.69,188.66) --
	(301.32,188.87) --
	(302.10,189.13) --
	(302.23,189.17) --
	(302.50,189.26) --
	(302.82,189.36) --
	(302.98,189.42) --
	(303.49,189.59) --
	(303.87,189.71) --
	(304.04,189.77) --
	(304.05,189.77) --
	(304.17,189.82) --
	(304.21,189.83) --
	(304.88,190.05) --
	(305.44,190.24) --
	(305.52,190.26) --
	(305.61,190.29) --
	(305.86,190.37) --
	(306.19,190.49) --
	(306.32,190.53) --
	(307.91,191.06) --
	(307.96,191.07) --
	(308.47,191.24) --
	(308.57,191.27) --
	(309.22,191.49) --
	(309.44,191.56) --
	(309.51,191.59) --
	(309.67,191.64) --
	(310.00,191.75) --
	(310.25,191.83) --
	(310.76,192.00) --
	(310.92,192.06) --
	(311.04,192.09) --
	(311.16,192.14) --
	(311.41,192.22) --
	(311.41,192.22) --
	(311.44,192.23) --
	(311.54,192.26) --
	(311.68,192.31) --
	(311.68,192.31) --
	(311.88,192.38) --
	(312.22,192.49) --
	(312.92,192.72) --
	(313.12,192.79) --
	(313.27,192.84) --
	(313.53,192.93) --
	(313.83,193.02) --
	(314.24,193.16) --
	(314.31,193.18) --
	(314.45,193.23) --
	(314.63,193.29) --
	(315.00,193.41) --
	(315.21,193.48) --
	(315.23,193.49) --
	(315.37,193.53) --
	(315.48,193.57) --
	(315.51,193.58) --
	(315.62,193.62) --
	(315.70,193.64) --
	(315.79,193.67) --
	(316.13,193.79) --
	(316.22,193.82) --
	(316.38,193.87) --
	(316.61,193.95) --
	(316.93,194.05) --
	(317.07,194.10) --
	(317.20,194.14) --
	(317.36,194.20) --
	(317.75,194.33) --
	(317.76,194.33) --
	(317.79,194.34) --
	(317.86,194.36) --
	(317.89,194.37) --
	(317.98,194.40) --
	(318.43,194.55) --
	(318.60,194.61) --
	(318.85,194.69) --
	(319.11,194.78) --
	(319.21,194.81) --
	(319.52,194.91) --
	(319.81,195.01) --
	(320.44,195.22) --
	(321.85,195.69) --
	(321.91,195.71) --
	(322.04,195.75) --
	(322.30,195.84) --
	(322.60,195.94) --
	(322.75,195.99) --
	(323.02,196.08) --
	(323.10,196.10) --
	(323.28,196.16) --
	(324.05,196.42) --
	(324.42,196.54) --
	(324.61,196.60) --
	(324.72,196.64) --
	(325.08,196.76) --
	(325.99,197.06) --
	(326.58,197.26) --
	(326.72,197.31) --
	(327.61,197.60) --
	(327.91,197.70) --
	(328.67,197.95) --
	(328.94,198.04) --
	(329.07,198.09) --
	(329.52,198.24) --
	(331.17,198.78) --
	(332.00,199.06) --
	(332.27,199.15) --
	(333.07,199.42) --
	(333.19,199.45) --
	(333.76,199.64) --
	(335.51,200.23) --
	(336.07,200.41) --
	(336.75,200.64) --
	(336.88,200.68) --
	(337.54,200.90) --
	(337.92,201.03) --
	(338.29,201.15) --
	(338.32,201.16) --
	(338.37,201.17) --
	(338.79,201.32) --
	(338.87,201.34) --
	(339.41,201.52) --
	(339.54,201.56) --
	(340.26,201.80) --
	(340.28,201.81) --
	(340.36,201.84) --
	(340.58,201.91) --
	(340.90,202.02) --
	(341.07,202.07) --
	(341.38,202.18) --
	(341.48,202.21) --
	(341.53,202.23) --
	(341.57,202.24) --
	(342.00,202.38) --
	(342.06,202.40) --
	(342.60,202.58) --
	(342.92,202.69) --
	(344.39,203.18) --
	(344.81,203.31) --
	(345.03,203.39) --
	(345.51,203.55) --
	(345.56,203.56) --
	(346.27,203.80) --
	(348.09,204.40) --
	(348.19,204.44) --
	(348.32,204.48) --
	(348.52,204.55) --
	(348.65,204.59) --
	(350.04,205.05) --
	(350.29,205.13) --
	(350.39,205.17) --
	(351.49,205.53) --
	(354.19,206.43) --
	(354.41,206.50) --
	(354.96,206.69) --
	(354.99,206.69) --
	(355.28,206.79) --
	(355.84,206.98) --
	(356.71,207.27) --
	(356.75,207.28) --
	(357.50,207.53) --
	(357.53,207.54) --
	(358.04,207.71) --
	(358.62,207.90) --
	(359.31,208.13) --
	(359.62,208.23) --
	(359.75,208.28) --
	(359.85,208.31) --
	(360.61,208.56) --
	(360.64,208.57) --
	(360.71,208.60) --
	(361.91,208.99) --
	(362.60,209.22) --
	(364.24,209.77) --
	(364.46,209.84) --
	(365.70,210.25) --
	(366.29,210.45) --
	(370.53,211.86) --
	(371.02,212.02) --
	(372.06,212.37) --
	(372.07,212.37) --
	(372.38,212.47) --
	(372.60,212.54) --
	(372.90,212.65) --
	(373.16,212.73) --
	(373.53,212.86) --
	(373.80,212.94) --
	(374.46,213.16) --
	(374.81,213.28) --
	(375.77,213.60) --
	(376.36,213.80) --
	(376.51,213.85) --
	(376.93,213.98) --
	(378.03,214.35) --
	(379.36,214.79) --
	(379.36,214.79) --
	(380.09,215.03) --
	(380.12,215.04) --
	(381.03,215.35) --
	(381.47,215.49) --
	(381.75,215.58) --
	(382.36,215.79) --
	(382.44,215.82) --
	(382.57,215.86) --
	(383.02,216.01) --
	(385.04,216.68) --
	(385.16,216.72) --
	(388.87,217.95) --
	(393.56,219.51) --
	(395.71,220.22) --
	(403.26,222.73) --
	(404.02,222.98);

@@

\path[fill=fillColor,fill opacity=0.30] ( 52.97,167.36) --
	( 61.01,168.41) --
	( 65.48,168.80) --
	( 65.62,168.81) --
	( 79.64,170.79) --
	( 88.50,171.79) --
	( 94.41,172.49) --
	( 97.84,173.06) --
	(104.50,173.98) --
	(110.01,174.56) --
	(113.94,175.03) --
	(116.56,175.36) --
	(124.94,176.30) --
	(160.01,181.27) --
	(160.15,181.30) --
	(163.56,181.70) --
	(164.50,181.78) --
	(175.08,183.35) --
	(177.68,183.86) --
	(185.12,185.40) --
	(195.04,187.30) --
	(195.05,187.30) --
	(199.79,188.52) --
	(200.09,188.60) --
	(201.70,188.94) --
	(202.42,189.05) --
	(203.15,189.18) --
	(203.24,189.19) --
	(203.92,189.29) --
	(204.08,189.32) --
	(205.70,189.71) --
	(211.30,190.89) --
	(213.02,191.21) --
	(213.22,191.26) --
	(213.28,191.27) --
	(214.88,191.68) --
	(219.39,192.70) --
	(219.87,192.77) --
	(224.51,193.76) --
	(226.38,194.26) --
	(226.89,194.38) --
	(228.22,194.75) --
	(229.80,195.15) --
	(230.53,195.25) --
	(231.54,195.47) --
	(232.29,195.59) --
	(232.55,195.66) --
	(232.60,195.67) --
	(233.03,195.77) --
	(236.50,196.61) --
	(238.44,197.03) --
	(239.50,197.27) --
	(240.76,197.54) --
	(242.87,198.03) --
	(243.82,198.26) --
	(244.87,198.51) --
	(245.90,198.81) --
	(247.14,199.15) --
	(247.15,199.15) --
	(248.00,199.39) --
	(248.59,199.55) --
	(249.15,199.72) --
	(249.91,199.94) --
	(250.14,200.00) --
	(250.71,200.16) --
	(251.21,200.29) --
	(251.61,200.40) --
	(251.88,200.46) --
	(252.52,200.69) --
	(252.98,200.84) --
	(253.12,200.86) --
	(253.36,200.89) --
	(254.91,201.29) --
	(255.02,201.32) --
	(256.32,201.72) --
	(258.61,202.38) --
	(260.03,202.80) --
	(260.14,202.84) --
	(260.80,203.04) --
	(261.97,203.27) --
	(262.19,203.35) --
	(262.48,203.44) --
	(262.99,203.62) --
	(264.29,204.03) --
	(264.50,204.10) --
	(264.53,204.11) --
	(264.97,204.25) --
	(266.10,204.54) --
	(266.13,204.55) --
	(266.44,204.61) --
	(267.28,204.93) --
	(267.71,205.05) --
	(268.38,205.26) --
	(269.11,205.45) --
	(269.74,205.69) --
	(269.87,205.74) --
	(271.02,206.18) --
	(271.10,206.22) --
	(271.68,206.47) --
	(272.40,206.66) --
	(272.79,206.78) --
	(273.63,207.07) --
	(274.52,207.40) --
	(275.28,207.68) --
	(275.59,207.78) --
	(276.13,207.95) --
	(276.31,207.99) --
	(276.77,208.14) --
	(277.30,208.37) --
	(277.98,208.66) --
	(278.04,208.68) --
	(278.45,208.79) --
	(279.17,208.98) --
	(279.30,209.02) --
	(279.52,209.08) --
	(279.66,209.14) --
	(279.69,209.14) --
	(280.15,209.31) --
	(280.53,209.48) --
	(280.72,209.56) --
	(281.20,209.75) --
	(281.36,209.82) --
	(281.45,209.85) --
	(282.80,210.34) --
	(283.05,210.37) --
	(283.89,210.70) --
	(283.98,210.74) --
	(284.07,210.78) --
	(284.62,210.98) --
	(284.86,211.08) --
	(285.03,211.13) --
	(285.13,211.16) --
	(286.00,211.42) --
	(286.57,211.61) --
	(286.59,211.61) --
	(287.25,211.79) --
	(287.81,211.98) --
	(288.54,212.28) --
	(288.59,212.29) --
	(289.22,212.44) --
	(289.76,212.64) --
	(290.76,213.08) --
	(290.86,213.13) --
	(291.20,213.21) --
	(291.32,213.21) --
	(291.81,213.42) --
	(291.88,213.46) --
	(292.21,213.58) --
	(292.36,213.65) --
	(292.42,213.69) --
	(292.49,213.72) --
	(292.51,213.74) --
	(292.62,213.79) --
	(293.21,213.98) --
	(293.91,214.28) --
	(295.25,214.70) --
	(295.45,214.78) --
	(295.51,214.81) --
	(295.93,215.00) --
	(295.99,215.02) --
	(296.10,215.06) --
	(296.47,215.21) --
	(296.65,215.26) --
	(296.99,215.30) --
	(297.01,215.30) --
	(297.04,215.31) --
	(297.05,215.31) --
	(297.09,215.32) --
	(297.13,215.34) --
	(297.22,215.39) --
	(297.31,215.44) --
	(297.31,215.44) --
	(297.71,215.55) --
	(297.96,215.64) --
	(298.34,215.77) --
	(298.57,215.86) --
	(299.04,216.04) --
	(300.58,216.50) --
	(300.69,216.54) --
	(301.32,216.72) --
	(302.10,216.99) --
	(302.23,217.04) --
	(302.50,217.16) --
	(302.82,217.32) --
	(302.98,217.40) --
	(303.49,217.63) --
	(303.87,217.81) --
	(304.04,217.89) --
	(304.05,217.89) --
	(304.17,217.95) --
	(304.21,217.97) --
	(304.88,218.27) --
	(305.44,218.51) --
	(305.52,218.55) --
	(305.61,218.58) --
	(305.86,218.68) --

>>>>

% Created by tikzDevice version 0.7.0 on 2014-10-09 04:51:36
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,105.13) --
	( 61.01,108.04) --
	( 65.48,109.65) --
	( 65.62,109.70) --
	( 79.64,114.78) --
	( 88.50,117.99) --
	( 94.41,120.13) --
	( 97.84,121.37) --
	(104.50,123.78) --
	(110.01,125.77) --
	(113.94,127.20) --
	(116.56,128.15) --
	(124.94,131.18) --
	(160.01,143.88) --
	(160.15,143.93) --
	(163.56,145.16) --
	(164.50,145.50) --
	(175.08,149.33) --
	(177.68,150.27) --
	(185.12,152.97) --
	(195.04,156.56) --
	(195.05,156.56) --
	(199.79,158.28) --
	(200.09,158.39) --
	(201.70,158.97) --
	(202.42,159.23) --
	(203.15,159.49) --
	(203.24,159.53) --
	(203.92,159.77) --
	(204.08,159.83) --
	(205.70,160.42) --
	(211.30,162.45) --
	(213.02,163.07) --
	(213.22,163.14) --
	(213.28,163.16) --
	(214.88,163.74) --
	(219.39,165.37) --
	(219.87,165.55) --
	(224.51,167.23) --
	(226.38,167.90) --
	(226.89,168.09) --
	(228.22,168.57) --
	(229.80,169.14) --
	(230.53,169.41) --
	(231.54,169.77) --
	(232.29,170.04) --
	(232.55,170.14) --
	(232.60,170.16) --
	(233.03,170.31) --
	(236.50,171.57) --
	(238.44,172.27) --
	(239.50,172.65) --
	(240.76,173.11) --
	(242.87,173.87) --
	(243.82,174.22) --
	(244.87,174.60) --
	(245.90,174.97) --
	(247.14,175.42) --
	(247.15,175.43) --
	(248.00,175.73) --
	(248.59,175.94) --
	(249.15,176.15) --
	(249.91,176.42) --
	(250.14,176.51) --
	(250.71,176.71) --
	(251.21,176.89) --
	(251.61,177.04) --
	(251.88,177.14) --
	(252.52,177.37) --
	(252.98,177.54) --
	(253.12,177.58) --
	(253.36,177.67) --
	(254.91,178.23) --
	(255.02,178.27) --
	(256.32,178.74) --
	(258.61,179.57) --
	(260.03,180.09) --
	(260.14,180.13) --
	(260.80,180.37) --
	(261.97,180.79) --
	(262.19,180.87) --
	(262.47,180.97) --
	(262.99,181.16) --
	(264.29,181.63) --
	(264.50,181.70) --
	(264.53,181.72) --
	(264.97,181.88) --
	(266.10,182.28) --
	(266.13,182.29) --
	(266.44,182.41) --
	(267.28,182.71) --
	(267.71,182.87) --
	(268.38,183.11) --
	(269.11,183.37) --
	(269.74,183.60) --
	(269.87,183.65) --
	(271.02,184.07) --
	(271.10,184.09) --
	(271.68,184.30) --
	(272.40,184.56) --
	(272.79,184.71) --
	(273.63,185.01) --
	(274.52,185.33) --
	(275.28,185.61) --
	(275.59,185.72) --
	(276.13,185.92) --
	(276.31,185.98) --
	(276.77,186.15) --
	(277.30,186.34) --
	(277.98,186.59) --
	(278.04,186.61) --
	(278.45,186.76) --
	(279.17,187.02) --
	(279.30,187.06) --
	(279.52,187.14) --
	(279.66,187.19) --
	(279.69,187.20) --
	(280.15,187.37) --
	(280.53,187.51) --
	(280.72,187.58) --
	(281.20,187.75) --
	(281.36,187.81) --
	(281.45,187.84) --
	(282.80,188.33) --
	(283.05,188.42) --
	(283.89,188.73) --
	(283.98,188.76) --
	(284.07,188.79) --
	(284.62,188.99) --
	(284.86,189.08) --
	(285.03,189.14) --
	(285.13,189.17) --
	(286.00,189.49) --
	(286.57,189.69) --
	(286.59,189.70) --
	(287.25,189.94) --
	(287.81,190.14) --
	(288.54,190.41) --
	(288.59,190.43) --
	(289.22,190.65) --
	(289.76,190.85) --
	(290.76,191.21) --
	(290.86,191.25) --
	(291.20,191.37) --
	(291.32,191.41) --
	(291.81,191.59) --
	(291.88,191.62) --
	(292.21,191.74) --
	(292.36,191.79) --
	(292.42,191.81) --
	(292.49,191.84) --
	(292.51,191.85) --
	(292.62,191.89) --
	(293.21,192.10) --
	(293.91,192.35) --
	(295.25,192.84) --
	(295.45,192.91) --
	(295.51,192.93) --
	(295.93,193.08) --
	(295.99,193.10) --
	(296.10,193.14) --
	(296.47,193.28) --
	(296.65,193.34) --
	(296.99,193.47) --
	(297.01,193.47) --
	(297.04,193.49) --
	(297.05,193.49) --
	(297.09,193.50) --
	(297.13,193.52) --
	(297.22,193.55) --
	(297.31,193.58) --
	(297.31,193.58) --
	(297.71,193.73) --
	(297.96,193.82) --
	(298.34,193.96) --
	(298.57,194.04) --
	(299.04,194.21) --
	(300.58,194.77) --
	(300.69,194.81) --
	(301.32,195.03) --
	(302.10,195.32) --
	(302.23,195.36) --
	(302.50,195.46) --
	(302.82,195.58) --
	(302.98,195.63) --
	(303.49,195.82) --
	(303.87,195.96) --
	(304.04,196.02) --
	(304.05,196.02) --
	(304.17,196.07) --
	(304.21,196.08) --
	(304.88,196.32) --
	(305.44,196.53) --
	(305.52,196.56) --
	(305.61,196.59) --
	(305.86,196.68) --
	(306.19,196.80) --
	(306.32,196.84) --
	(307.91,197.42) --
	(307.96,197.44) --
	(308.47,197.62) --
	(308.57,197.66) --
	(309.22,197.89) --
	(309.44,197.97) --
	(309.51,198.00) --
	(309.67,198.06) --
	(310.00,198.18) --
	(310.25,198.27) --
	(310.76,198.45) --
	(310.92,198.51) --
	(311.04,198.55) --
	(311.16,198.60) --
	(311.41,198.69) --
	(311.41,198.69) --
	(311.44,198.70) --
	(311.54,198.73) --
	(311.68,198.78) --
	(311.68,198.79) --
	(311.88,198.86) --
	(312.22,198.98) --
	(312.92,199.23) --
	(313.12,199.31) --
	(313.27,199.36) --
	(313.53,199.46) --
	(313.83,199.56) --
	(314.24,199.71) --
	(314.31,199.74) --
	(314.45,199.79) --
	(314.63,199.85) --
	(315.00,199.99) --
	(315.21,200.06) --
	(315.23,200.07) --
	(315.37,200.12) --
	(315.48,200.16) --
	(315.51,200.17) --
	(315.62,200.21) --
	(315.70,200.24) --
	(315.79,200.27) --
	(316.13,200.40) --
	(316.22,200.43) --
	(316.38,200.49) --
	(316.61,200.57) --
	(316.93,200.69) --
	(317.07,200.74) --
	(317.20,200.78) --
	(317.36,200.84) --
	(317.75,200.98) --
	(317.76,200.99) --
	(317.79,201.00) --
	(317.86,201.02) --
	(317.89,201.03) --
	(317.98,201.06) --
	(318.43,201.23) --
	(318.60,201.29) --
	(318.85,201.38) --
	(319.11,201.48) --
	(319.21,201.51) --
	(319.52,201.62) --
	(319.81,201.73) --
	(320.44,201.96) --
	(321.85,202.47) --
	(321.91,202.49) --
	(322.04,202.54) --
	(322.30,202.63) --
	(322.60,202.74) --
	(322.75,202.79) --
	(323.02,202.89) --
	(323.10,202.92) --
	(323.28,202.99) --
	(324.05,203.26) --
	(324.42,203.40) --
	(324.61,203.47) --
	(324.72,203.51) --
	(325.08,203.64) --
	(325.99,203.97) --
	(326.58,204.18) --
	(326.72,204.23) --
	(327.61,204.55) --
	(327.91,204.66) --
	(328.67,204.94) --
	(328.94,205.03) --
	(329.07,205.08) --
	(329.52,205.25) --
	(331.17,205.84) --
	(332.00,206.14) --
	(332.27,206.24) --
	(333.07,206.53) --
	(333.19,206.57) --
	(333.76,206.78) --
	(335.51,207.41) --
	(336.07,207.61) --
	(336.75,207.86) --
	(336.88,207.91) --
	(337.54,208.15) --
	(337.92,208.29) --
	(338.29,208.42) --
	(338.32,208.43) --
	(338.37,208.45) --
	(338.79,208.60) --
	(338.87,208.63) --
	(339.41,208.82) --
	(339.54,208.87) --
	(340.26,209.13) --
	(340.28,209.14) --
	(340.36,209.17) --
	(340.58,209.25) --
	(340.90,209.36) --
	(341.07,209.43) --
	(341.38,209.54) --
	(341.48,209.58) --
	(341.53,209.59) --
	(341.57,209.61) --
	(342.00,209.76) --
	(342.06,209.78) --
	(342.60,209.98) --
	(342.92,210.09) --
	(344.39,210.63) --
	(344.81,210.78) --
	(345.03,210.86) --
	(345.51,211.03) --
	(345.56,211.05) --
	(346.27,211.31) --
	(348.09,211.97) --
	(348.19,212.00) --
	(348.32,212.05) --
	(348.52,212.12) --
	(348.65,212.17) --
	(350.04,212.67) --
	(350.29,212.76) --
	(350.39,212.80) --
	(351.49,213.20) --
	(354.19,214.18) --
	(354.41,214.26) --
	(354.96,214.45) --
	(354.99,214.46) --
	(355.28,214.57) --
	(355.84,214.77) --
	(356.71,215.09) --
	(356.75,215.10) --
	(357.50,215.37) --
	(357.53,215.38) --
	(358.04,215.57) --
	(358.62,215.78) --
	(359.31,216.03) --
	(359.62,216.14) --
	(359.75,216.19) --
	(359.85,216.23) --
	(360.61,216.50) --
	(360.64,216.51) --
	(360.71,216.54) --
	(361.91,216.97) --
	(362.60,217.22) --
	(364.24,217.81) --
	(364.46,217.89) --
	(365.70,218.34) --
	(366.29,218.56) --
	(370.53,220.09) --
	(371.02,220.27) --
	(372.06,220.65) --
	(372.07,220.65) --
	(372.38,220.76) --
	(372.60,220.84) --
	(372.90,220.95) --
	(373.16,221.04) --
	(373.53,221.18) --
	(373.80,221.27) --
	(374.46,221.51) --
	(374.81,221.64) --
	(375.77,221.99) --
	(376.36,222.20) --
	(376.51,222.26) --
	(376.93,222.41) --
	(378.03,222.80) --
	(379.36,223.29) --
	(379.36,223.29) --
	(380.09,223.55) --
	(380.12,223.56) --
	(381.03,223.89) --
	(381.47,224.05) --
	(381.75,224.15) --
	(382.36,224.37) --
	(382.44,224.40) --
	(382.57,224.45) --
	(383.02,224.61) --
	(385.04,225.34) --
	(385.16,225.39) --
	(388.87,226.73) --
	(393.56,228.43) --
	(395.71,229.21) --
	(403.26,231.94) --
	(404.02,232.22);

@@

\path[fill=fillColor,fill opacity=0.30] ( 52.97,166.87) --
	( 61.01,168.28) --
	( 65.48,168.86) --
	( 65.62,168.88) --
	( 79.64,170.96) --
	( 88.50,172.39) --
	( 94.41,173.16) --
	( 97.84,173.62) --
	(104.50,174.54) --
	(110.01,175.23) --
	(113.94,175.72) --
	(116.56,176.32) --
	(124.94,177.43) --
	(160.01,182.90) --
	(160.15,182.92) --
	(163.56,183.58) --
	(164.50,183.75) --
	(175.08,185.58) --
	(177.68,186.03) --
	(185.12,187.31) --
	(195.04,188.98) --
	(195.05,188.98) --
	(199.79,189.84) --
	(200.09,189.94) --
	(201.70,190.33) --
	(202.42,190.48) --
	(203.15,190.65) --
	(203.24,190.66) --
	(203.92,190.82) --
	(204.08,190.85) --
	(205.70,191.15) --
	(211.30,192.32) --
	(213.02,192.64) --
	(213.22,192.68) --
	(213.28,192.70) --
	(214.88,193.02) --
	(219.39,194.06) --
	(219.87,194.20) --
	(224.51,195.24) --
	(226.38,195.65) --
	(226.89,195.79) --
	(228.22,196.10) --
	(229.80,196.48) --
	(230.53,196.69) --
	(231.54,196.92) --
	(232.29,197.08) --
	(232.55,197.15) --
	(232.60,197.16) --
	(233.03,197.26) --
	(236.50,198.18) --
	(238.44,198.69) --
	(239.50,198.96) --
	(240.76,199.23) --
	(242.87,199.83) --
	(243.82,200.10) --
	(244.87,200.43) --
	(245.90,200.74) --
	(247.14,201.06) --
	(247.15,201.07) --
	(248.00,201.30) --
	(248.59,201.43) --
	(249.15,201.55) --
	(249.91,201.77) --
	(250.14,201.82) --
	(250.71,201.96) --
	(251.21,202.07) --
	(251.61,202.15) --
	(251.88,202.21) --
	(252.52,202.37) --
	(252.98,202.49) --
	(253.12,202.52) --
	(253.36,202.58) --
	(254.91,202.96) --
	(255.02,202.98) --
	(256.32,203.27) --
	(258.61,203.82) --
	(260.03,204.14) --
	(260.14,204.17) --
	(260.80,204.35) --
	(261.97,204.65) --
	(262.19,204.76) --
	(262.47,204.86) --
	(262.99,205.01) --
	(264.29,205.28) --
	(264.50,205.34) --
	(264.53,205.35) --
	(264.97,205.48) --
	(266.10,205.84) --
	(266.13,205.85) --
	(266.44,205.95) --
	(267.28,206.24) --
	(267.71,206.41) --
	(268.38,206.62) --
	(269.11,206.90) --
	(269.74,207.05) --
	(269.87,207.08) --
	(271.02,207.45) --
	(271.10,207.48) --
	(271.68,207.67) --
	(272.40,207.84) --
	(272.79,207.97) --
	(273.63,208.21) --
	(274.52,208.52) --
	(275.28,208.71) --
	(275.59,208.84) --
	(276.13,209.05) --
	(276.31,209.10) --
	(276.77,209.23) --
	(277.30,209.42) --
	(277.98,209.63) --
	(278.04,209.66) --
	(278.45,209.79) --
	(279.17,210.00) --
	(279.30,210.03) --
	(279.52,210.12) --
	(279.66,210.17) --
	(279.69,210.17) --
	(280.15,210.36) --
	(280.53,210.49) --
	(280.72,210.53) --
	(281.20,210.70) --
	(281.36,210.76) --
	(281.45,210.80) --
	(282.80,211.27) --
	(283.05,211.35) --
	(283.89,211.61) --
	(283.98,211.65) --
	(284.07,211.68) --
	(284.62,211.85) --
	(284.86,211.90) --
	(285.03,211.93) --
	(285.13,211.96) --
	(286.00,212.24) --
	(286.57,212.41) --
	(286.59,212.42) --
	(287.25,212.62) --
	(287.81,212.79) --
	(288.54,213.02) --
	(288.59,213.02) --
	(289.22,213.26) --
	(289.76,213.50) --
	(290.76,213.87) --
	(290.86,213.92) --
	(291.20,214.07) --
	(291.32,214.11) --
	(291.81,214.26) --
	(291.88,214.29) --
	(292.21,214.39) --
	(292.36,214.45) --
	(292.42,214.48) --
	(292.49,214.51) --
	(292.51,214.52) --
	(292.62,214.56) --
	(293.21,214.80) --
	(293.91,215.07) --
	(295.25,215.52) --
	(295.45,215.58) --
	(295.51,215.61) --
	(295.93,215.78) --
	(295.99,215.79) --
	(296.10,215.81) --
	(296.47,215.93) --
	(296.65,215.99) --
	(296.99,216.12) --
	(297.01,216.13) --
	(297.04,216.14) --
	(297.05,216.14) --
	(297.09,216.16) --
	(297.13,216.17) --
	(297.22,216.21) --
	(297.31,216.24) --
	(297.31,216.24) --
	(297.71,216.36) --
	(297.96,216.42) --
	(298.34,216.59) --
	(298.57,216.66) --
	(299.04,216.81) --
	(300.58,217.39) --
	(300.69,217.46) --
	(301.32,217.75) --
	(302.10,218.06) --
	(302.23,218.10) --
	(302.50,218.21) --
	(302.82,218.31) --
	(302.98,218.37) --
	(303.49,218.57) --
	(303.87,218.74) --
	(304.04,218.82) --
	(304.05,218.82) --
	(304.17,218.88) --
	(304.21,218.90) --
	(304.88,219.13) --
	(305.44,219.34) --
	(305.52,219.36) --
	(305.61,219.38) --
	(305.86,219.46) --
	(306.19,219.59) --
